CF Registry Analysis

### 2025-06-12 Christine Chan/CF Registry/cf_registry_survival_analysis.qmd
WNAR background finished

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(knitr)
library(eulerr)
library(broom)
library(emmeans)
library(ggstats)
library(patchwork)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Linux" = "/home/timvigers/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

>>>>

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(knitr)
library(eulerr)
library(broom)
library(emmeans)
library(ggstats)
library(patchwork)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Linux" = "/home/timvigers/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

# Write cleaned data
save(annual,file = "./Data_Clean/survival_dataset.RData")
